Refinements for open pNets

### 2021-07-29 2021-Refinement/paper/refinementarticle.tex
comment section 4.2

We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
	\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array}} \\
	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\end{definition}
Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$. Note also the second part of the conjunction of condition 2 expresses the deadlock reduction between automata.

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update.

>>>>

We define here simulation between labelled transition systems to Hole-equal simulation  between  open automata that have exactly the same holes.
\begin{definition}[Hole-equal simulation]
Consider two OAs \(\OAg[1]\) and \(\OAg[2]\) with  \(J_1 = J_2\), the relation on configurations \(R: S_1 \times S_2 \to \rformulas[V_1 \uplus V_2]\) is a hole-\(\symb{equal}\) simulation from $S_1$ to $S_2$ if the following conditions hold: 
\item[(1)] \(\sigma_{01} \uplus \sigma_{02} \vdash R\mpar{s_{01}, s_{02}}\)
\item[(2)] \(\forall \mpar{s_1, s_2} \in S_1 \times S_2,\)\vspace{-8pt}
\noindent\begin{multline*}
\mpar{\everymath{\displaystyle}\begin{array}{l}
		\bigsymb{\forall} t_1 = \OTx{1}{}{1}{1} \in \fOT{s_1}, \bigsymb{\exists} \mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X}, \\
		\quad \mpar{\forall x \in X, J'_{2x}= J'_1} \\[-10pt]
		\nwedge V_1 \uplus V_2 \uplus \fvars{t_1} \vdash \left( R\mpar{s_1, s_2} \wedge g_1 \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\begin{array}{l}
			\alpha_1 = \alpha_{2x} \wedge \bigwedge_\subbox{j \in J'_{2x} \cap J_1} \beta_{1j} = \beta_{2xj} \\[12pt]
			\nwedge g_{2x} \wedge R\mpar{s'_1, s'_{2x}}\psubst{\psi_1 \uplus \psi_{2x}}
		\end{array}}\right)
	\end{array}} \\
	\wedge \mpar{V_1 \uplus V_2 \uplus \biguplus_\subbox{t_2 \in \fOT{s_2}} \fvars{t_2} \vdash R\mpar{s_1, s_2} \wedge \bigvee_\subbox{t_2 \in \fOT{s_2}} \fguard{t_2} \implies \bigvee_\subbox{t_1 \in \fOT{s_1}} \fguard{t_1}}
\end{multline*}
\end{definition}
Note in this definition, instead of matching an instantiated transition of the first automata to another instantiated transition of the second, it matches an open transition $t_1$ to a family of covering open transitions $t_{2x}^{x\in X}$. Note also the second part of the conjunction of condition (2) expresses the deadlock reduction between automata (as introduced in Definition \ref{def:dpwd}).

Intuitively, this means that for every pair of related
states $(s_1,s_2)$  of the two automata, and for every  transition of the first automaton from $s_1$, there is a set of matching transitions  of the second automaton  from $s_2$ such that the produced action match, the actions of the same holes and the successors are related after variable update. Our definition captures a simple kind of sub-classing of open automata with the same holes. It is stronger than a strict simulation since it matches a transition with a family of transitions. With such a relation we are able to check the refinement between two open automata corresponding to the same component but specified differently, for example, by duplicating states, removing transitions,  reinforcing  guards, modifying variables, etc...

%Technically,  it expresses how the concepts from the abstract and the refined systems are linked together.
